%% start of file `template.tex'.
%% Copyright 2006-2013 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[11pt,a4paper,sans]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')

% moderncv themes
\moderncvstyle{casual}                             % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue}                               % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
%\renewcommand{\familydefault}{\sfdefault}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
%\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page

% character encoding
\usepackage[utf8]{inputenc}                       % if you are not using xelatex ou lualatex, replace by the encoding you are using
%\usepackage{CJKutf8}                              % if you need to use CJK to typeset your resume in Chinese, Japanese or Korean

% adjust the page margins
\usepackage[scale=0.75]{geometry}
%\setlength{\hintscolumnwidth}{3cm}                % if you want to change the width of the column with the dates
%\setlength{\makecvtitlenamewidth}{10cm}           % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...

% personal data
\name{Taejoong}{Chung}
\title{Postdoctoral Researcher (t.chung@neu.edu)}
%\address{805 Columbus Avenue}{Boston, MA }{United States}% optional, remove / comment the line if not wanted; the "postcode city" and and "country" arguments can be omitted or provided empty
%\email{t.chung@neu.edu}                               % optional, remove / comment the line if not wanted
%\homepage{taejoong.github.io}                         % optional, remove / comment the line if not wanted
%\extrainfo{additional information}                 % optional, remove / comment the line if not wanted
%\photo[64pt][0.4pt]{picture}                       % optional, remove / comment the line if not wanted; '64pt' is the height the picture must be resized to, 0.4pt is the thickness of the frame around it (put it to 0pt for no frame) and 'picture' is the name of the picture file
%\quote{Some quote}                                 % optional, remove / comment the line if not wanted

% to show numerical labels in the bibliography (default is to show no labels); only useful if you make citations in your resume
%\makeatletter
%\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
%\makeatother
%\renewcommand*{\bibliographyitemlabel}{[\arabic{enumiv}]}% CONSIDER REPLACING THE ABOVE BY THIS

% bibliography with mutiple entries
%\usepackage{multibib}
%\newcites{book,misc}{{Books},{Others}}
%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
%\begin{CJK*}{UTF8}{gbsn}                          % to typeset your resume in Chinese using CJK
%-----       resume       ---------------------------------------------------------
\makecvtitle

\vspace{-1cm}
\section{Education}
\cventry{09/2009--02/2015}{Ph.D.}{Computer Science and Engineering, Seoul National University}{Seoul}{Korea}{
    \begin{itemize}%
    \item \footnotesize Thesis: ``\emph{Analytic Approach of Understanding Crowd Phenomnea on the Internet: Case Studies of MMORPG and BitTorrent}''
    \item Supervisors: {Prof. Yanghee Choi} and {Prof. Ted ``Taekyoung'' Kwon}
    \end{itemize}
}
\cventry{03/2005--09/2009}{B.S.}{Computer Science and Enginnering, POSTECH (Pohang University of Science and Technology)}{Pohang}{Korea}{}

\section{Professional Experiences}
\cventry{09/2015--present}{Postdoctoral Researcher}{Northeastern University, Boston, MA}{United States}{}{}
\cventry{03/2015--02/2016}{Postdoctoral Researcher}{Seoul National University, Seoul}{Korea}{}{}
\cventry{06/2013--03/2014}{Research Intern}{Cisco Systems}{Cambridge, MA}{United States}{}{}
\cventry{08/2011--02/2015}{Research Assistant}{Seoul National University, Seoul}{Korea}{}{}
\cventry{09/2011--12/2011}{Teaching Assistant}{Seoul National University, Seoul}{Korea}{}{
    \begin{itemize}
        \item Computer Networks (4190.411, Fall 2011)
    \end{itemize}
}
\cventry{09/2010--12/2010}{Teaching Assistant}{Seoul National University, Seoul}{Korea}{}{
    \begin{itemize}
        \item Engineering Math II (400.002A, Fall 2010)
    \end{itemize}
}
\cventry{03/2010--06/2010}{Teaching Assistant}{Seoul National University, Seoul}{Korea}{}{
    \begin{itemize}
        \item Engineering Math I (400.001A, Spring 2010)
    \end{itemize}
}

\section{Honors and Awards}
\cvitem{2017}{Distinguished Paper Award, USENIX Security'17}
\cvitem{2015}{Microsoft Azure Research ``Award Program: Microsoft Azure for Research Supports \$20,000''}
\cvitem{2010}{Best Paper Award, Korea Information and Communication Society (KICS)}
\cvitem{2010}{Best Paper Award, IEEE Communication Society Seoul Chapter}

\section{Grants}
\cvitem{2015}{Personal Recommendation System and Privacy Protection through Big Data Analysis on Online Social Networks}
\cvlistitem{(PI) Research Grant of Basic Science Research Program by National Research Foundation of Korea (NRF) funded by the Ministry of Education (2015018668)}

\section{Refereed Journal Publications}
\publication{CSCW'17}{Privacy Leakage in Event-based Social Networks: A Meetup Case Study}{\textcolor{colortj}{T. Chung}, J. Han, D. Choi, T. Kwon, J. Rha, and H. Kim}{CSCW, Jersey City, USA, Nov. 2018}

\publication{IMC'17}{Understanding the Role of Registrars in DNSSEC Deployment}{\textcolor{colortj}{T. Chung}, R. van Rijswijk-Deij, D. Choffnes, A. Mislove, C. Wilson, D. Levin, and B. M. Maggs}{IMC, London, UK, Nov. 2017}

\publication{USENIX Security'17}
{A Longitudinal, End-to-End View of the DNSSEC Ecosystem}
{\textcolor{colortj}{T. Chung}, R. van Rijswijk-Deij, B. Chandrasekaran, D. Choffnes, D. Levin, B. M. Maggs, A. Mislove, and C. Wilson}
{USENIX Security, Vancouver, Canada, Aug. 2017}

\publication{IMC'16}
{Measuring and Applying Invalid SSL Certificates: The Silent Majority}
{\textcolor{colortj}{T. Chung}, Y. Liu, D. Choffnes, D. Levin, B. M. Maggs, A. Mislove, and C. Wilson}
{IMC, Santa Monica, CA, USA, Nov. 2016}

\publication{IMC'16}
{Tunneling for Transparency: A Large-Scale Analysis of End-to-End Violations in the Internet}
{\textcolor{colortj}{T. Chung}, D. Choffnes, and A. Mislove}
{IMC, Santa Monica, CA, USA, Nov. 2016}

\publication{CCS'16}
{Measurement and Analysis of Private Key Sharing in the HTTPS Ecosystem}
{F. Cangialosi, \textcolor{colortj}{T. Chung}, D. Choffnes, D. Levin, B. M. Maggs, A. Mislove, and C. Wilson}
{CCS, Vienna, Austria, Oct. 2016}

\publication{COSN'15}
{Characterizing Conversation Patterns in Reddit: From the Perspectives of Content Properties and User Participation Behaviors}
{D. Choi, J. Han, \textcolor{colortj}{T. Chung}, Y. Ahn, B. Chun, and T. Kwon}
{COSN, Stanford, CA, USA, Nov. 2015}


\publication{COSN'15}
{Sharing Topics in Pinterest: Under- standing Content Creation and Diffusion Behaviors}
{J. Han, D. Choi, A. Choi, \textcolor{colortj}{T. Chung}, T. Kwon, J. Rha, and C. Chuah}
{COSN, Stanford, CA, USA, Nov. 2015}


\publication{ANCS'14}
{CoRC: Coordinated Routing and Caching for Named Data Networking}
{H. Choi, J. Yoo, \textcolor{colortj}{T. Chung}, N. Choi, T. Kwon, and Y. Choi}
{ANCS, Marina del Rey, CA, USA, Oct. 2014 }

\publication{WWW'14}
{Unveiling Group Characteristics in Online Social Games: A Socio-Economic Analysis}
{\textcolor{colortj}{T. Chung}, J. Han, D. Choi, T. Kwon, H. K. Kim and Y. Choi}
{WWW, Seoul, Korea, Apr. 2014}

\publication{IFIP Networking'13}
{Spatial and Temporal Locality of Content in BitTorrent: A Measurement Study}
{\textcolor{colortj}{T. Chung}, J. Han, H. Lee, J. Kangasharju, T. Kwon, and Y. Choi}
{IFIP Networking, Brooklyn, NY, USA, May 2013 }

\publication{SIGMETRICS'12}
{Bundling Practice in Bittorrent: What, How, and Why}
{J. Han, S. Kim, \textcolor{colortj}{T. Chung}, T. Kwon, H. Kim, and Y. Choi}
{SIGMETRICS, London, UK, Jun. 2012}

\publication{IFIP Networking'12}
{Content Publishing and Downloading Practice in BitTorrent}
{S. Kim, J. Han, \textcolor{colortj}{T. Chung}, T. Kwon, H. Kim, and Y. Choi}
{IFIP Networking, Prague, Czech, May 2012}

\publication{GLOBECOM'12}
{Bandwidth Allocation for BitTorrent under Multi-Torrent Environments}
{J. Choi, J. Han, \textcolor{colortj}{T. Chung}, E. Cho, T. Kwon, and Y. Choi}
{GLOBECOM, Houston, Texas, United States, Dec. 2011}. 

\section{Journal Publications}
\publication{}
{A Target-centric Surveillance System based on Localization and Social Networking
}
{J. Han, N. Choi, \textcolor{colortj}{T. Chung}, T. Kwon, and Y. Choi}
{Multimedia Tools and Applications (MTAP), Vol. 73, Issue 1, pp. 241-265, Nov. 2014}

\publication{}
{Strategic Bundling for Content Availability and Fast Distribution in BitTorrent}
{J. Han, \textcolor{colortj}{T. Chung}, S. Kim, H. Kim, J. Kangasharju, T. Kwon, and Y. Choi}
{Computer Communication (COMCOM), Vol. 43, pp. 64-73, May 2014}


\publication{}
{Bundling Practice in Bittorrent: What, How, and Why}
{J. Han, S. Kim, \textcolor{colortj}{T. Chung}, T. Kwon, H. Kim, and Y. Choi}
{ACM SIGMETRICS Performance Evaluation Review, Vol. 40, No. 1, pp. 77-88, Jun. 2012.}

\publication{}
{How Prevalent is Content Bundling in BitTorrent? }
{J. Han, \textcolor{colortj}{T. Chung}, S. Kim, T. Kwon, H. Kim, and Y. Choi}
{ACM SIGMETRICS Performance Evaluation Review, Vol. 39, No. 1, pp. 319-320, Jun. 2011.}

\section{Posters}
\publication{SIGCOMM'17}
{The Root Canary: Monitoring and Measuring the DNSSEC Root Key Rollover}
{R. van Rijswijk-Deij, \textcolor{colortj}{T. Chung}, D. Choffnes, A. Mislove, and W. Toorop}
{SIGCOMM, Los Angeles, CA, USA, Aug. 2017}

\publication{ACNS'14}
{Toward Terabyte-scale Caching with SSD in a Named Data Networking Router}
{W. So, \textcolor{colortj}{T. Chung}, H. Yuan, D. Oran, and M. Stapp}
{ANCS, Marina del Rey, CA, USA, Oct. 2014 }

\publication{PAM'13}
{Spatial and Temporal Locality of Swarm Dynamics in BitTorrent}
{\textcolor{colortj}{T. Chung}, J. Han, H. Lee, J. Kangasharju, T. Kwon, and Y. Choi}
{PAM, Hong Kong, March. 2013.}

\section{Non-Refereed Journal Publications}
\publication{TPRC'17}
{Investigating End-To-End Integrity Violations in Internet Traffic}
{A. Mislove, D. Choffnes, and \textcolor{colortj}{T. Chung}}
{TPRC, Arlington, VA, USA, Sept. 2017}

\section{Fellowships}
\cventry{2012--2016}{Samsung Ph.D. Industrial Scholarship}{}{}{}{}{}
\cventry{2010--2012}{Hyundai (Hajung) Scholarship}{}{}{}{}{}
\cventry{Summer 2007}{POSTECH Student Exchange Program to UCLA}{}{}{}{}{}
\cventry{2005--2008}{National Science \& Technology Scholarship, KOSAF(Korea Student Aid Foundation)} {}{}{}{}{}


\section{Project Experience}
\project{06/2015--06/2016}{Personal Recommendation System and Privacy Protection through Big Data Analysis on Online Social Networks}
{National Research Foundation of Korea (NRF)}{}{}

\project{09/2012--06/2013}{Networking Content Delivery Optimization}
{SAMSUNG Electronics}{}{}

\project{03/2011--02/2014}{Fundamental Research on In-network Caching and Routing for Named-data Networking}
{Korea Communications Agency (KCA)}{}{}

\project{07/2010--12/2012}{Future Internet Service Demonstration: Internet Video Diary}
{Korea Internet \& Security Agency (KISA), Korea }{}{}

\section{Service}
\cventry{}{Program Committee Member}{}{}{}{}
\cvitem{'14}{Poster Selection Committee of ACM/IEEE Symposium on Architectures for Networking and Communications Systems (ANCS)}

\cventry{}{Shadow Program Committee Member}{}{}{}{}
\cvitem{'17}{ACM Internet Measurement Conference (IMC)}

\section{Talks}
\cvitem{09/08/2017}{Research Conference on Communications, Information and Internet Policy (TPRC)}
\cvitem{08/18/2017}{USENIX Security}
\cvitem{11/16/2016}{ACM Internet Measurement Conference (IMC)}
\cvitem{11/15/2016}{ACM Internet Measurement Conference (IMC)}
\cvitem{10/07/2016}{New England Networking and Systems Day (NENS)}
\cvitem{12/29/2014}{Korea Advanced Institute of Science and Technology (KAIST)}
\cvitem{04/10/2014}{World Wide Web Conference (WWW)}
\cvitem{05/22/2013}{IFIP Networking}
\cvitem{12/07/2011}{IEEE GLOBECOM}


\section{References}

\project{}{Alan Mislove (amislove@ccs.neu.edu)}{Associate Professor of Computer Science, Northeastern University, USA}{}{}

\project{}{David Choffnes (choffnes@ccs.neu.edu)}{Assistant Professor of Computer Science, Northeastern University, USA}{}{}

\project{}{Dave Oran (daveoran@orandom.net)}{Former fellow at Cisco Systems, USA}{}{}

\project{}{Ted ``Taekyoung'' Kwon (tkkwon@snu.ac.kr)}{Professor, School of Computer Science \& Engineering, Seoul National University}{}{}

\project{}{Yanghee Choi (yhchoi@snu.ac.kr)}{Professor, School of Computer Science \& Engineering, Seoul National University, Korea (leave of absence)}{}{}


% Publications from a BibTeX file without multibib
%  for numerical labels: \renewcommand{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}% CONSIDER MERGING WITH PREAMBLE PART
%  to redefine the heading string ("Publications"): \renewcommand{\refname}{Articles}
\nocite{*}
\bibliographystyle{plain}
\bibliography{publications}                        % 'publications' is the name of a BibTeX file
\end{document}


%% end of file `template.tex'.
